Well Hello There!

### 2024-10-11 index.qmd
update
update

## My Hello to You \~

@@

@media screen and (max-width: 600px) {
  .tiktok-embed {
    min-width: auto;
  }
}
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">

<section>

<a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>

<p>overland travel for the vibesss</p>

<a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>

</section>

</blockquote>

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
> </blockquote>

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7238779076528442625" data-video-id="7238779076528442625" style="max-width: 605px;min-width: 325px;">

<section>

<a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>

<p>nha trang is my favvvvvv</p>

<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>

</section>

</blockquote>

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
:::

@@

@@

![](docs/src/images/brochure.png)

### Design Thinking

In this module, we were assigned the task of innovating everyday chores. Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe!

![](images/prototyping.png){fig-align="center"}

The actual prototyping journey was not very smooth, but hey, here is the end product! Looks good aye? To me at least...

![](images/prototyping_2-01.png)

## Temasek Polytechnic

>>>>

## My Hello to You \~\~

@@

@media screen and (max-width: 600px) {
  .tiktok-embed {
    min-width: auto;
  }
}
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">
    <section>
        <a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>
        <p>overland travel for the vibesss</p>
        <a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>
    </section>
</blockquote>

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">
    <section>
        <a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>
        <p>errr i drank about 9 cups of pearl milk tea in 4 days 3 nights 🇹🇼🥴🧋🇹🇼</p>
        <a target="_blank" title="♬ fish in the pool・花屋敷 - ヘクとパスカル" href="https://www.tiktok.com/music/fish-in-the-pool-花屋敷-6910585281334740994?refer=embed">♬ fish in the pool・花屋敷 - ヘクとパスカル</a>
    </section>
</blockquote>

<script async src="https://www.tiktok.com/embed.js"></script>
:::

@@

### Digital Storytelling

During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind. He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.

{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}

@@

::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">

</iframe>
:::

<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>

### Temasek Polytechnic
